Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-29 paper/paper.tex
paper edits Tested everything on quipu.

We have found that the deterministic simulations of the protein
reaction sequence discussed above results in robust oscillatory
behavoir of polar selection and oscillation in not only symmetrical
shapes, such as the wild type pill shape, but also in very
assymetrical, flatttened cells, such as those studied by Mannik.  This
differs with Mannik's experimental findings that show much less
regular behavoir, with a large variation in the location of maxima.
On the other hand, our stochastic simulations show both robust pole to
pole oscillations in the symmetric cells and irregular behavoir in the
assymetrical shapes, agreeing well with Mannik's experimental
findings.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{../paper/plot-ave}
  \caption{Arrows depicting global maxima in space and local maxima in
    time overlayed on color plots of time averaged total MinD density.
    A density threshold is chosen and only maxima above this threshold
    are shown. The plots serve to illistrate what is observed in our
    movies.  At this point the data is over varying amounts of time
    but its all roughly 1000 seconds\fixme{fix this}.  The top row
    shows plots published by Mannik of the MinD maxima behavoir and
    the bottom two rows show our pancake shapes that are designed to
    have the same shape.  The middle row shows results from the
    stochastic simulation and the bottom shows results from the
    deterministic.  We can see that the stochastic method shows
    behavoir that is similar to experiment while the deterministic
    method shows maximization that is too regular and robust.}
  \label{randst-plot-ave}
\end{figure}

>>>>

We have found that the deterministic simulations of the protein
reaction sequence discussed above results in robust oscillatory
behavoir of polar selection and oscillation in not only symmetrical
shapes, such as the wildtype pill shape, but also in very
assymetrical, flatttened cells, such as those studied by Mannik.
After the lower stability limit of
section~\ref{sec:stability-analysis} has been surpassed, this
qualitative behavoir doesn't seem to have size dependence until cells
reach sizes that have more than twice the dimensions of the Mannik
cells.  At this point the robust oscillations, while still evident,
begin to lose their consistanty.  The Mannik reported cells already
seem to be rather large (wild type cells are typically smaller than
those observed my Mannik
\cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}),
so we left off simulating cells any larger than twice this size.

This differs with Mannik's experimental findings
that show much less regular behavoir, with a large variation in the
location of maxima.  On the other hand, our stochastic simulations
show both robust pole to pole oscillations in the symmetric cells and
irregular behavoir in the assymetrical shapes, agreeing well with
Mannik's experimental findings.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{../paper/plot-ave}
  \caption{Arrows depicting global maxima in space and local maxima in
    time overlayed on color plots of time averaged total MinD density.
    A density threshold is chosen and only maxima above this threshold
    are shown. The plots serve to illistrate what is observed in our
    movies.  The simulation time covered in these is 1000 seconds
    \fixme{this is not true yet - need to change the data once its
      finished right now 2 of them are 1000 the others are like 980}.
    The top row shows plots published by Mannik of the MinD maxima
    behavoir and the bottom two rows show our pancake shapes that are
    designed to have the same shape.  The middle row shows results
    from the stochastic simulation and the bottom shows results from
    the deterministic.  We can see that the stochastic method shows
    behavoir that is similar to experiment while the deterministic
    method shows maximization that is too regular and robust.}
  \label{randst-plot-ave}
\end{figure}
